Caribou Demographi Projection - interesting & informative title TBD

### 2022-12-05 analysis/paper/paper.Rmd
tweaks

Also following [@eacker_web-based_2019], Kaplan-Meier estimates of observed adult female survival probability $\hat{S}_t$ and associated precisions $\tau_t$ are estimated from known-fate radio collar data using the survival R package [@terry_m_therneau_modeling_2000], with precisions for years with no observed mortality estimated using a separate Bayesian model. Observed survival is a Gaussian distributed function of the true survival probability: $$\hat{S_t} \sim \text{normal}(S_t,1/\tau_t).$$ 
We model true survival probability as an adjusted function of anthropogenic disturbance  [@johnson_science_2020;@stewart_climate-informed_nodate;@dyson_existing_2022], with a log link and Gaussian distributed random year effect [@eacker_web-based_2019]: $$S_t=\text{min}(46 S_{adj,t}-0.5)/45,1); \log(S_{adj,t})=\beta^S_0+\beta^S_a anthro_t+\epsilon^S_t; \epsilon^S_t \sim \text{normal}(0,\sigma^2_{S,e}).$$ 
To assess sensitivity of results to the survival estimation method, we also implemented an alternative parametric exponential survival model, wherein the state of an individual animal in year $t$ and month $m$ is Bernoulli distributed (ref IPM book): $$A_{t,m} \sim \text{Bernoulli}(S^{1/12}_tA_{t,m-1}).$$

@@

TO DO: ensure that INF_saf_INF_r_JAGS_extentTime.txt and INF_saf_INF_r_JAGS_expSurvival2.txt are identical except for the survival observation model. Or better yet, write code to sub in correct survival model more elegantly.
TO DO: note various bits of truncation in the JAGS code to ensure R and S remain between 0 and 1 (not guaranteed give log link). Not all documented in this explanation. Bayesian wizard might know a better way. Or at least know how to explain.
TO DO: note Eacker survival method gives biased results in years when <12 months of survival data is available.
TO DO: Note I am dropping survival information for animals that are not alive at the beginning of a year to deal with censoring issues. There is probably some more elegant way to deal with this, but it won't make any difference as long as the collar deployment month is set to 1.
TO DO: add references to documentation of popGrowthJohnson and other caribouMetrics functions.

>>>>

Also following [@eacker_web-based_2019], Kaplan-Meier estimates of observed adult female survival probability $\hat{S}_t$ and associated precisions $\tau_t$ are estimated from known-fate radio collar data using the survival R package [@therneau_modeling_2000], with precisions for years with no observed mortality estimated using a separate Bayesian model. Observed estimated survival is a Gaussian distributed function of the true survival probability: $$\hat{S_t} \sim \text{normal}(S_t,1/\tau_t).$$ 
We model true survival probability as an adjusted function of anthropogenic disturbance  [@johnson_science_2020;@stewart_climate-informed_nodate;@dyson_existing_2022], with a log link and Gaussian distributed random year effect [@eacker_web-based_2019]: $$S_t=\text{min}(46 \tilde{S_t}-0.5)/45,1); \log(\tilde{S_t})=\beta^S_0+\beta^S_a anthro_t+\epsilon^S_t; \epsilon^S_t \sim \text{normal}(0,\sigma^2_{S,e}).$$ 
To assess sensitivity of results to the survival estimation method, we also implemented an alternative parametric exponential survival model, wherein the state of an individual animal in year $t$ and month $m$ is Bernoulli distributed (ref IPM book): $$A_{t,m} \sim \text{Bernoulli}(S^{1/12}_t A_{t,m-1}).$$

@@

TO DO:

* ensure that INF_saf_INF_r_JAGS_extentTime.txt and INF_saf_INF_r_JAGS_expSurvival2.txt are identical except for the survival observation model. Or better yet, write code to sub in correct survival model more elegantly.
* note various bits of truncation in the JAGS code to ensure R and S remain between 0 and 1 (not guaranteed given log link). Not all documented in this explanation. Bayesian wizard might know a better way. Or at least know how to explain.
* note Eacker survival method gives biased results in years when <12 months of survival data is available.
* Note I am dropping survival information for animals that are not alive at the beginning of a year to deal with censoring issues. There is probably some more elegant way to deal with this, but it won't make any difference as long as the collar deployment month is set to 1.
* add references to documentation of popGrowthJohnson and other caribouMetrics functions.
